The impact of environmental shocks on children's schooling in Bolivia

### 2020-05-06 paper_draft.Rmd
working on the region variable code for valleys, line 592

```
```{r summary statistic tables with total_subset data, echo = F, message = F}
#creating a table with the main explanatory variables

@@

>>>>

```{r summary stats example}
install.packages("stargazer")
library(stargazer)

stargazer(total_subset)

```{r create summary statistic table, echo = F, results = 'asis'}
#creating a table with the main explanatory variables

load("processed-data/analysis_data.RData")

stargazer::stargazer(as.data.frame(stat_data),
                     label = "summaryStats",
                     title = "Summary statistics",
                     header = F,
                     type = "latex",
                     digits = 0)

@@

```
\begin{table}
\centering
\caption{Variable definitions}
\label{variableDefinitions}
\begin{tabular}{ll}
\hline
\hline
Variable name      & Description                                   \\
\hline
svr\_mean          & Monthly mean of SVR at a park                 \\
svr\_median        & Monthly median of SVR at a park               \\
svr\_p10           & Monthly 10th percentile of SVR at a park      \\
svr\_p25           & Monthly 25th percentile of SVR at a park      \\
svr\_p75           & Monthly 75th percentile of SVR at a park      \\
svr\_p90           & Monthly 90th percentile of SVR at a park      \\
recreation\_visits & Monthly number of recreation visits at a park \\
\hline
\end{tabular}
\end{table}
